\begin{thebibliography}{99}

\bibitem{gammaWeb}
Crowd and Multi-agent Simulation. \textit{Gamma: Geometric Algorithms for Modeling, Motion, and Animation} [online]. [cit. 2017-05-04]. Dostupné z: http://gamma.cs.unc.edu/research/crowds/

\bibitem{Colorni1991}
COLORNI, Alberto, Marco DORIGO a Vittorio MANIEZZO. \textit{Distributed Optimization by Ant Colonies} [online]. ACM SIGGRAPH Symposium on Interactive 3D Graphics and Games (I3D), 1991, , 12 [cit. 2017-05-04]. Dostupné z: https://scholar.google.com/citations?view\_op\=view\_citation\&hl\=cs\&user\=PwYT6EMAAAAJ\&citation\_for\_view\=PwYT6EMAAAAJ\:2osOgNQ5qMEC

\bibitem{Blum2005}
BLUM, Christian. Ant colony optimization: Introduction and recent trends. In: \textit{Https://www.sciencedirect.com} [online]. 2005 [cit. 2017-05-05]. Dostupné z: https://www.ics.uci.edu/~welling/teaching/271fall09/antcolonyopt.pdf

\bibitem{ReynoldsBoid}
REYNOLDS, Craig. Boids: Background and Update. In: \textit{Reynolds Engineering \& Design} [online]. 1995 [cit. 2017-05-03]. Dostupné z: http://www.red3d.com/cwr/boids/

\bibitem{ReynoldsBoidNoBump}
REYNOLDS, Craig. Not Bumping Into Things. In: \textit{Reynolds Engineering \& Design} [online]. 1988 [cit. 2017-05-03]. Dostupné z: http://www.red3d.com/cwr/nobump/nobump.html

\bibitem{Unity}
\textit{Unity 3D} [online]. [cit. 2017-05-04]. Dostupné z: https://unity3d.com

\bibitem{Golas2013}
GOLAS, Abhinav, Rahul NARAIN a Ming LIN. \textit{Hybrid Long-Range Collision Avoidance for Crowd Simulation} [online]. ACM SIGGRAPH Symposium on Interactive 3D Graphics and Games (I3D), 2013, , 7 [cit. 2017-05-04]. Dostupné z: http://gamma.cs.unc.edu/lookahead/golas-2013-hybridcrowd.pdf

\end{thebibliography}